Marlowe: implementing and analysing financial contracts on blockchain

### 2019-12-10 papers/marlowe2019/paper.tex
Add commas

\texttt{Observation}s are Boolean expressions that compare values, and can be combined using the standard Boolean operators. It is also possible to observe whether any choice has been made (for a particular identified choice).

\texttt{Action}s, unlike \texttt{Observation}s, which have a value at every step of execution, happen at particular points during execution and can be:
(i) depositing money, (ii)
making a choice between various alternatives, or (iii)
notifying the contract that a certain observation has become true.

@@

\texttt{Close}: A contract \texttt{Close} provides for the contract to be closed (or terminated). The only action that is performed is to refund the contents of each account to their respective owners. This is performed one account per step, but all accounts will be refunded in a single transaction.

@@

Marlowe is specified by an executable semantics written in Haskell, but to make it usable in practice to execute financial contracts, it needs to be implemented on a blockchain. In this section we explain how Marlowe is executed on the Cardano blockchain using an interpreter written in the Plutus programming language.

@@

To implement Marlowe contracts we use the PlutusTx compiler,
which compiles Haskell code into serialized \emph{Plutus Core} code,
to create a Cardano \emph{validator script} that ensures the correct execution of the contract.
This form of implementation relies on the extensions to the UTxO model described in~\cite{PlutusPlatform}.

>>>>

\texttt{Observation}s are Boolean expressions that compare values, and can be combined using the standard Boolean operators. It is also possible to observe whether any choice has been made (for a particular identified choice). Observations will have a value at every step of execution.

\texttt{Action}s happen at particular points during execution and can be (i) depositing money, (ii) making a choice between various alternatives, or (iii) notifying the contract that a certain observation has become true.

@@

\texttt{Close}: A contract \texttt{Close} provides for the contract to be closed (or terminated). The only action that is performed is to refund the contents of each account to their respective owners. This is performed one account per step, but all accounts will be refunded in a single transaction. All contracts eventually reduce to \texttt{Close}.

@@

Marlowe is specified by an executable semantics written in Haskell, but to make it usable in practice to execute financial contracts, it needs to be implemented on a blockchain. In this section, we explain how Marlowe is executed on the Cardano blockchain using an interpreter written in the Plutus programming language.

@@

To implement Marlowe contracts, we use the PlutusTx compiler,
which compiles Haskell code into serialized \emph{Plutus Core} code,
to create a Cardano \emph{validator script} that ensures the correct execution of the contract.
This form of implementation relies on the extensions to the UTxO model described in~\cite{PlutusPlatform}.
